Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-03 paper/paper.tex
fixed frames.
fixed minor spacing issues.

\begin{figure}[t!]
  \psset{unit=1mm}
  \begin{pspicture}(90,48)(0,-48)
    %\psframe(90,48)(0,-48)
    \begin{tabular}{@{}c@{}}
      \psframebox{\sf
	\renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
            \UFL\
            \UNL{0} (\DEFINE\ (\length\  \pl)
	    \UNL{1}  (\SIF~(\NULLQ \ \pl) $0$
            (\PRIM\ 1\ (\CAR\  \pl))))
            \UNL{0}
	    \UNL{0}  (\DEFINE\ (\append\  \lista\ \listb)
	    \UNL{1}  (\SIF~(\NULLQ \ \lista)
	    \listb
	    \UNL{2} \hspace*{-0.1cm}(\CONS\ (\CAR\  \lista) (\append\
            (\CDR\  \lista)
            \listb))))
            \UNL{0}
            \UNL{0} (\LET\ \px\
            $\leftarrow$\ (\CONS\ $5$
            (\CONS\ (\CONS\ $6$ \NIL) \NIL) \IN
	    \UNL{1} (\LET\ \py\   $\leftarrow$\  (\CONS\ $3$ \NIL) \IN
	    \UNL{2}
            (\LET\ \pz\  $\leftarrow$\  (\append\ \px\  \py)\ \IN\
            \UNL{3} (\SIF~(\NULLQ~(\CAR~(\CDR~\pz)))~$0$~$\pi$:\
            (\length\ \pz))))))
	  \end{uprogram}
      }}
      \\ 
      (a) Example program. \\  \\
%      \includegraphics[width=.45\textwidth]{motiv-example}
      \input{mem-graph} \\ 
      \renewcommand{\arraystretch}{.9}
      \begin{tabular}[t]{l}
        (b) Memory graph at $\pi$. Thick edges denote live
        links. Traversal \\{\white (b)} stops at edges
        marked $\times$ during garbage collection.
      \end{tabular}
    \end{tabular} 
  \end{pspicture}
  \vspace*{-3ex}
  \caption{Example Program and its Memory Graph}\label{fig:mot-example}
\end{figure}

@@

\begin{figure}[t]
\footnotesize
\begin{eqnarray*}
   p \in \mathit{Prog} & ::= & d_1 \ldots d_n \,\, e_\mainpgm
    \hspace{5em} \mbox{\em --- program}\\
    \mathit{df} \in Fdef & ::= & (\DEFINE\,\, (f\,\, x_1 \,\, \ldots
\,\,x_n)\,\,
    e)
    \hspace{0.2em} \ \ \ \ \mbox{\em --- function definition} \\
e \in \mathit{Expr} & ::= &
\left\{\begin{array}{@{}ll@{\hspace{2em}}l}
       (\SIF\,\, x\,\, e_1\,\, e_2) && \!\!\!\mbox{\em --- conditional} \\
       (\LET\,\, x \leftarrow s\,\, \IN\,\, e) &&\!\!\! \mbox{\em --- let
binding} \\
       (\SRETURN\,\, x) && \!\!\!\mbox{\em --- return from function}
    \end{array}\right. \\
s \in \mathit{Application} & ::= &
\left\{\begin{array}{@{}l@{\hspace{1.2em}}l}
       k & \mbox{\em --- constant (numeric or $\NIL$)}\\
       (\CONS\,\, x_1\,\, x_2) & \mbox{\em --- constructor} \\
       (\CAR\,\, x) & \\
       (\CDR\,\, x) & \mbox{\em --- selectors} \\
       (\NULLQ\,\, x) & \\
       (\PRIM\,\, x_1\,\, x_2) & \mbox{\em ---  tester
and generic arithmetic} \\
       (\ID\,\, x) & \mbox{\em ---  identity function (for inlining)} \\
\\
       (f\,\, x_1\,\,\ldots\,\, x_n) & \mbox{\em --- function application}
    \end{array}\right.
\end{eqnarray*}
  \caption{The syntax of our language}\label{fig:lang-syntax}
\figrule
\normalsize
\end{figure}

>>>>

\begin{figure}[t!]
  \psset{unit=1mm}
  \begin{pspicture}(90,48)(0,-48)
    %\psframe(90,48)(0,-48)
    \begin{tabular}{@{}c@{}}
      %\psframebox
          {\sf
	\renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
            \UFL\
            \UNL{0} (\DEFINE\ (\length\  \pl)
	    \UNL{1}  (\SIF~(\NULLQ \ \pl) $0$
            (\PRIM\ 1\ (\CAR\  \pl))))
            \UNL{0}
	    \UNL{0}  (\DEFINE\ (\append\  \lista\ \listb)
	    \UNL{1}  (\SIF~(\NULLQ \ \lista)
	    \listb
	    \UNL{2} \hspace*{-0.1cm}(\CONS\ (\CAR\  \lista) (\append\
            (\CDR\  \lista)
            \listb))))
            \UNL{0}
            \UNL{0} (\LET\ \px\
            $\leftarrow$\ (\CONS\ $5$
            (\CONS\ (\CONS\ $6$ \NIL) \NIL) \IN
	    \UNL{1} (\LET\ \py\   $\leftarrow$\  (\CONS\ $3$ \NIL) \IN
	    \UNL{2}
            (\LET\ \pz\  $\leftarrow$\  (\append\ \px\  \py)\ \IN\
            \UNL{3} (\SIF~(\NULLQ~(\CAR~(\CDR~\pz)))~$0$~$\pi$:\
            (\length\ \pz))))))
	  \end{uprogram}
      }}
      \\ 
      (a) Example program. \\  \\
%      \includegraphics[width=.45\textwidth]{motiv-example}
      \input{mem-graph} \\ 
      \renewcommand{\arraystretch}{.9}
      \begin{tabular}[t]{l}
        (b) Memory graph at $\pi$. Thick edges denote live
        links. Traversal \\{\white (b)} stops at edges
        marked $\times$ during garbage collection.
      \end{tabular}
    \end{tabular} 
  \end{pspicture}
  \vspace*{-3ex}
  \caption{Example Program and its Memory Graph}\label{fig:mot-example}
\end{figure}

@@

\begin{figure}[t]
\footnotesize
\begin{eqnarray*}
   p \in \mathit{Prog} & \!\!\!::=\!\!\! & d_1 \ldots d_n \,\, e_\mainpgm
    \hspace{5em} \mbox{\em --- program}\\
    \mathit{df} \in Fdef & \!\!\!::=\!\!\! & (\DEFINE\,\, (f\,\, x_1 \,\, \ldots
\,\,x_n)\,\,
    e)
    \hspace{0.2em} \ \ \ \ \mbox{\em --- function definition} \\
e \in \mathit{Expr} & \!\!\!::=\!\!\! &
\left\{\begin{array}{@{}ll@{\hspace{2em}}l}
       (\SIF\,\, x\,\, e_1\,\, e_2) && \!\!\!\mbox{\em --- conditional} \\
       (\LET\,\, x \leftarrow s\,\, \IN\,\, e) &&\!\!\! \mbox{\em --- let
binding} \\
       (\SRETURN\,\, x) && \!\!\!\mbox{\em --- return from function}
    \end{array}\right. \\
s \in \mathit{App} & \!\!\!::=\!\!\!  &
\left\{\begin{array}{@{}l@{\hspace{1.2em}}l}
       k & \mbox{\em --- constant (numeric or $\NIL$)}\\
       (\CONS\,\, x_1\,\, x_2) & \mbox{\em --- constructor} \\
       (\CAR\,\, x) & \\
       (\CDR\,\, x) & \mbox{\em --- selectors} \\
       (\NULLQ\,\, x) & \\
       (\PRIM\,\, x_1\,\, x_2) & \mbox{\em ---  tester
and generic arithmetic} \\
       (\ID\,\, x) & \mbox{\em ---  identity function (for inlining)} \\
       (f\,\, x_1\,\,\ldots\,\, x_n) & \mbox{\em --- function application}
    \end{array}\right.
\end{eqnarray*}
  \caption{The syntax of our language}\label{fig:lang-syntax}
\figrule
\normalsize
\end{figure}
